Explore resilience evi

### 2017-11-24 analysis/evi/explore_resilience.Rmd
update

  out_ratr_df <- data.frame(var = c(out_raTrimmed$varnames[2], 
                                    out_raTrimmed$varnames[3], 
                                    paste0(out_raTrimmed$varnames[2], ':', out_raTrimmed$varnames[3])),
              statistic = c(out_raTrimmed$Qa, out_raTrimmed$Qb, out_raTrimmed$Qab),
              pvalue = c(out_raTrimmed$A.p.value, out_raTrimmed$B.p.value, out_raTrimmed$AB.p.value))

@@

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_pairwise.csv'), row.names = F)
write.csv(trimmedanovas, file=paste0(di, '/out/anovas_resilience/huber_evi/trimmed_anovas.csv', row.names = F)
```

>>>>

  out_ratr_df <- data.frame(fact = c(out_raTrimmed$varnames[2], 
                                    out_raTrimmed$varnames[3], 
                                    paste0(out_raTrimmed$varnames[2], ':', out_raTrimmed$varnames[3])),
              statistic = c(out_raTrimmed$Qa, out_raTrimmed$Qb, out_raTrimmed$Qab),
              pvalue = c(out_raTrimmed$A.p.value, out_raTrimmed$B.p.value, out_raTrimmed$AB.p.value))

@@

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/huber_evi/robust_pairwise.csv'), row.names = F)
write.csv(trimmedanovas, file=paste0(di, '/out/anovas_resilience/huber_evi/trimmed_anovas.csv'), row.names = F)
```
